[![](./images/lindens.jpg)](https://en.wikipedia.org/wiki/Tilia) An Application of LIME to a Random Forest

### 2019-03-01 presentations/graphics group/An Application of LIME to a Random Forest.Rmd
final edits to talk

---
title: "[![](./images/lindens.jpg)](https://en.wikipedia.org/wiki/Tilia) An Application of LIME to a Random Forest"
author: <font size="5"> Katherine Goode </font>
date: <font size="5"> ISU Graphics Group, March 1, 2019 </font>
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

- Can specify the number of features to select
    - We have been choosing 3 features
- Options in lime
     - auto: forward selection if $m\le6$, highest weight otherwise (default)
     - forward selection with ridge regression
     - highest weight with ridge regression
     - LASSO
     - tree models
- We have been using the default method

@@

- Since features are standardized, we can compare the coefficients
- Largest $\beta_i$ is considered the most important

@@

We first applied lime using all default settings.
- Explanations did not make sense
- $R^2$ values were very low
-Predictions from the simple model were poor

@@

Then we tried more of the feature distribution estimation methods
- explanations still not great
- $R^2$ values still very low
- predictions from the simple model still poor
- explanations dependent on the input

@@

- Apply LIME to a logistic regression model
    - We know how to interpret a logistic regression
    - Can compare to LIME explanations
- Run some sort of simulation to assess LIME explanations
- Adjust and compare weighting methods and the feature selection methods
- Allow the number of bins to vary across features
- Use a tree as the simple model

>>>>

---
title: "[![](./images/lindens.jpg)](https://en.wikipedia.org/wiki/Tilia) An Application of LIME to a Random Forest"
author: <font size="5"> Katherine Goode </font>
date: <font size="5"> ISU Graphics Group - March 1, 2019 </font>
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

- Can specify the number of features to select
    - We have been choosing 3 features
- Options in lime
     - auto: forward selection if $k\le6$, highest weight otherwise (default)
     - forward selection with ridge regression
     - highest weight with ridge regression
     - LASSO
     - tree models
- We have been using the default method

@@

- Since features are standardized, we can compare the coefficients
- Largest $\hat{\beta}_i$ is considered the most important

@@

We first applied lime using all default settings.
- Explanations did not make sense
- $R^2$ values were very low
- Predictions from the simple model were poor

@@

Then we tried more of the feature distribution estimation methods
- Explanations still not great
- $R^2$ values still very low
- Predictions from the simple model still poor
- Explanations dependent on the input

@@

- Apply LIME to a logistic regression model
    - We know how to interpret a logistic regression
    - Can compare to LIME explanations
- Run some sort of simulation to assess LIME explanations
- Adjust and compare weighting methods and the feature selection methods
- Allow the number of bins to vary across features
- Use a tree as the simple model
- Find other ways to interpret random forest models
